\def\det22#1#2#3#4{\left|\begin{matrix}#1 & #2\cr #3 & #4\end{matrix}\right|}

\section{Planar Geometry}

\subsection{Point and Line}
Point and line are the elementary objects in planar geometry.
Usually we use Cartesian coordinates to represent point and linear equations to
represent lines.

Every point on the real plane can be represented by a pair of real numbers
$(x, y)$ uniquely and vice versa. The pair $(x, y)$ is called the Cartesian
coordinates of the point.

Evey line on the real plane can be represented by a (but not unique) linear
equation $ax + by + c = 0$ where $ab \neq 0$. The equation $ax + by + c = 0$ can
be considered as a $3$-tuple of real numbers $(a, b, c)$. For $k \neq 0$,
$(ka, kb, kc)$ represents the same line. We use the symbol $[a : b : c]$ to
represent the line $ax + by + c = 0$ and call it the homogeneous coordinates of
line. Note that $[a : b : c] = [ka : kb : kc]$ for $k \neq 0$.

We can use the notation $[a : b : c]$ to define homogeneous coordinates for
planar points. For a point with Cartesian coordinates $(x, y)$, its homogeneous
coordinates is defined as $[x : y : 1]$. Note that $[zx : zy : z]$ where
$(z \neq 0)$ is the same homogeneous coordinates.

For two distinct points, there is a unique line passes them, and for two distinct
lines which are not parallel to each other, they intersect at exactly one point.
The equation of the line passes two points and the Cartesian
coordinates of intersection point of two lines can be computed by solving linear
equations. But there is a more beautiful solution when we use homogensous
coordinates and the notation of determinant.

The equation of the line passes $P(x_1,y_1)$ and $Q(x_2,y_2)$ is
$$\left|\begin{matrix}X&Y&1\cr x_1&y_1&1\cr x_2&y_2&1\end{matrix}\right|=0,$$
or equally
$$\left|\begin{matrix}y_1&1\cr y_2&1\end{matrix}\right|X
-\left|\begin{matrix}x_1&1\cr x_2&1\end{matrix}\right|Y
+\left|\begin{matrix}x_1&y_1\cr x_2&y_2\end{matrix}\right|=0,$$
and the intersection point of line $L(X,Y)=a_1X + b_1Y + c_1=0$ and $M(X,Y)=a_2X + b_2Y + c_2=0$ is
$$({{\left|\begin{matrix}b_1&c_1\cr b_2&c_2\end{matrix}\right|}\over d},
-{{\left|\begin{matrix}a_1&c_1\cr a_2&c_2\end{matrix}\right|}\over d}),$$
where $d = \det22{a_1}{b_1}{a_2}{b_2}$.
If we use homogeneous coordinates for points, the intersection point can be written as
\begin{equation*}
[ \det22{b_1}{c_1}{b_2}{c_2} :
- \det22{a_1}{c_1}{a_2}{c_2} :
  \det22{a_1}{b_1}{a_2}{b_2} ]
\end{equation*}

So we can define an operation $\times$ on the homogeneous coordinates by
\begin{equation*}
[a : b : c] \times [x : y : z]
= [ {\det22 b c y z} : {\det22 c a z x} : {\det22 a b x y} ]
\end{equation*}
It can compute the line passes two points and the intersection point of two
lines in an unified formula.

\subsection{Convex Hull}
